Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-15 ind_files/01_Introduction.tex
Minor phrasing changes

\begin{itemize}
	\item \textbf{Part \ref{part_theory}}
	develops mathematical formalism for describing finite fluctuating populations from first principles.
		\begin{itemize}
		\item Chapter \ref{chap_math_background} provides the necessary mathematical background and provides a toy example studying the size of a population of identical individuals that illustrates the major ideas used.
		\item Chapter \ref{chap_BD} develops a formalism for describing the evolution of finite fluctuating populations that vary in one or more \emph{discrete} traits. This yields equations that generalize the classic Price equation and replicator-mutator equation to finite fluctuating populations.
		\item Chapter \ref{chap_infD_processes} extends the ideas developed in chapter \ref{chap_BD} to populations that vary in a single one-dimensional \emph{quantitative} trait and derives so-called `stochastic field equations' that describe evolution in such populations. This also results in some new mathematical structures that may be of independent interest to mathematicians and physicists.
		\end{itemize}
	\item \textbf{Part \ref{part_summary}} presents the major results of this formalism.
		\begin{itemize}
			\item Chapter \ref{chap_unification} provides a technical summary of the major results in the form of three stochastic differential equations. These are equations for type frequencies, population mean value of an arbitrary type-level quantity, and population variance of an arbitrary type-level quantity, and respectively generalize the replicator-mutator equation, the Price equation/Fisher's fundamental theorem, and \cite{lion_theoretical_2018}'s variance equation to finite fluctuating populations.For finite populations, these equations predict a directional evolutionary force called `noise-induced selection' that is only seen in finite, fluctuating populations. Some implications for social evolution and community ecology are discussed.
			\item Section \ref{sec_disc_field_eqns} of chapter \ref{chap_unification} discusses the use of the stochastic field equations formulated in chapter \ref{chap_infD_processes}, connects them to some previous studies in biology, and briefly discusses the use of and knowledge about such mathematical objects in applied mathematics fields such as statistical physics. This section is quite technical due to the nature of the subject.
			\item Chapter \ref{sec_disc} provides a non-technical discussion and summary of all the major results, and discusses biological implications, connections with previous studies, and opportunities for future work. This chapter has no equations (!). The mathematically averse can skip all other chapters and only read chapter \ref{sec_disc} if they are interested only in the final results and takeaways\footnote{Though I promise I have tried my best to make sure the journey to this destination is also pleasant :)} 
		\end{itemize}
\end{itemize}

>>>>

\begin{itemize}
	\item \textbf{Part \ref{part_theory}}
	develops mathematical formalism for describing finite fluctuating populations from first principles.
		\begin{itemize}
		\item Chapter \ref{chap_math_background} provides the necessary mathematical background and provides a toy example studying the size of a population of identical individuals that illustrates the major ideas used.
		\item Chapter \ref{chap_BD} develops a formalism for describing the evolution of finite fluctuating populations that vary in one or more \emph{discrete} traits. This yields equations that generalize the classic Price equation and replicator-mutator equation to finite fluctuating populations.
		\item Chapter \ref{chap_infD_processes} extends the ideas developed in chapter \ref{chap_BD} to populations that vary in a single one-dimensional \emph{quantitative} trait and derives so-called `stochastic field equations' that describe evolution in such populations. This also results in some new mathematical structures that may be of independent interest to mathematicians and physicists.
		\end{itemize}
	\item \textbf{Part \ref{part_summary}} presents the major results of this formalism.
		\begin{itemize}
			\item Chapter \ref{chap_unification} provides a technical summary of the major results in the form of three stochastic differential equations. These are equations for type frequencies, population mean value of an arbitrary type-level quantity, and population variance of an arbitrary type-level quantity, and respectively generalize the replicator-mutator equation, the Price equation, and \cite{lion_theoretical_2018}'s variance equation to finite fluctuating populations. For finite populations, these equations predict a directional evolutionary force called `noise-induced selection' that is only seen in finite, fluctuating populations. Some implications for social evolution and community ecology are discussed.
			\item Section \ref{sec_disc_field_eqns} of chapter \ref{chap_unification} discusses the use of the stochastic field equations formulated in chapter \ref{chap_infD_processes}, connects them to some previous studies in biology, and briefly discusses the use of and knowledge about such mathematical objects in applied mathematics fields such as statistical physics. This section is quite technical due to the nature of the subject.
			\item Chapter \ref{sec_disc} provides a non-technical discussion and summary of all the major results, and discusses biological implications, connections with previous studies, and opportunities for future work. This chapter has no equations (!). The mathematically averse can skip all other chapters and only read chapter \ref{sec_disc} if they are interested only in the final results and takeaways\footnote{Though I promise I have tried my best to make sure the journey to this destination is also pleasant :)} 
		\end{itemize}
\end{itemize}
